### 2017-05-31 paper.tex
stab at #65

\fixme{65}{Write conclusion}

>>>>

Every day, university instructors and others are writing, teaching, sharing
lessons on subjects as diverse as history, biology, mathematics, or 
technical instruction. Our work overlaps, meaning thousands of hours of 
unnecessary duplication. In these ten simple rules, we provide an alternative: 
leveraging the model of collaborative software development to make more robust
and sustainable lessons that can be continually improved. We hope
that the lessons we provide here can help others learn from our experiences
to help us all teach better.
